The Name of the Title is Hope

### 2019-04-02 emsoft-2019/Motiv.tex
some updates

	where, $\theta$, $\omega$ and $u$ denote angular position, angular speed and input torque respectively; $g=9.81 m/s^2$ is the gravitional acceleration, $m$ the ball mass, $b$ the rotational fraction coefficient and $L$ the length of the bar. To design the controller, one has to first descretize the dynamics in $\eqref{eq:pendul_ss}$ with respect to an appropriate sample time $T_s$. Starting from an initial state, we would like the system's trajectory to converge into its equilibrium point while always $\theta\in[-\pi,\pi]$ and $\omega\in[-\pi/8,\pi/8]$. While there are many control schemes which can be used to stablize the system (e.g. LQR, state feedback), adding polytopic constraints, MPC schemes will be the best choice. 

@@

	However, one major challenge for implementing model predictive controllers over embedded systems will be to solve MPC optimality problem within each time step. Since the system under consideration is LTI, one can use explicit MPC scheme proposed in [Bemporad:2002] which computes partitions over state space together with affine functions which computes the optimal control input over their corresponding partition. For the inverted-pedulum example, the computed optimal control contains $14$ partitions shown in Fig \ref{fig:pendulum_reg}.

@@

	In practice, EMPC will be implemented over relatively low-price embedded systems which have limited memory capacity and computational power. Computing the optimal control input can be efficiently done using for example binary tree search. However, the memory limit is more serious as it increases proportional to the number of partitions.	Therefore, one direction is to explore ways to reduce required memory.
	On the other hand, most of the industrial embedded systems over which EMPC is implemented, only support fixed point arithmetic. Using fixed point arithmetic, will cause approximation error that is inversely proportional to the number of bits used. This approximation error must be considered since it might lead into violation of problem constraints. Therefore, one need to formulate the problem as robust MPC to count for disturbance input $|\omega|\leq \bar\omega$. Setting the number of bits for storing different variables, one can compute the upper bound for approximation error, $\bar\omega$. However, we would like to achieve the minimum number of bits that reduces memory requirements. To that end, one approach is to start with an initial $\bar \omega$; design an explicit robust MPC controller with respect to $\bar \omega$ and to use state of the art fixed-point error analyzers to decide for the number of required bits for saving each parameter. Again, back to inverted pendulum example, choosing $\bar \omega=0.1$, we design a robust MPC controller with partitions given in Fig. \ref{fig:pendulum_reg} (b). Now, in order to decide for the smallest number of bits, we use the floating point analysing tool, Daisy, to provide us with minimal uniform and mixed fixed-point reperesentation.

%	\begin{figure}
%		\includegraphics[width=.25\textwidth]{Figs/partition_order2_noise.eps};
%	\end{figure}

	\tikzstyle{block} = [draw, fill=blue!20, rectangle, 
	minimum height=3em, minimum width=6em]
	\tikzstyle{sum} = [draw, fill=blue!20, circle, node distance=1cm]
	\tikzstyle{input} = [coordinate]
	\tikzstyle{output} = [coordinate]
	\tikzstyle{pinstyle} = [pin edge={to-,thin,black}]
	\begin{figure*}[t]
		\begin{tikzpicture}[auto, node distance=2cm,>=latex',scale=1]
			\centering
			\node [block, pin={[pinstyle]above:$\delta=\delta_0$},
			node distance=5cm] (RMPC) {Robust MPC design};
			%\node[right of=RMPC](partitions){\includegraphics[width=.25\textwidth]{Figs/partition_order2_noise.pdf}};
			\node [block, right of=RMPC,
			node distance=5cm,text width=3cm] (mixed) {Mixed precision analysis};
			\node [draw, fill=blue!20, diamond, 
			minimum height=3em, minimum width=3em, right of=mixed,
			node distance=5cm] (decide) {Is memory violated?};
			\node [block, right of=decide,
			node distance=3cm] (done) {Done};
			\node [block, below of= decide,
			node distance=3cm] (delta) {increase $\delta$};

			\draw [draw,->] (RMPC) -- node [pos=-.1] {}(mixed);
			\draw [->] (mixed) -- node [name=aaa] {}(decide);
			\draw [->] (decide) -- node [above,pos=.3] {Yes} (done);
			\draw [->] (decide) -- node[pos=0.99] {} 
			node [] {No} (delta);
			\draw [->] (delta) -| node [above] {$\delta$} (RMPC);

>>>>

	where, $\theta$, $\omega$ and $u$ denote angular position, angular speed and input torque respectively; $g=9.81 m/s^2$ is the gravitational acceleration, $m$ the ball mass, $b$ the rotational fraction coefficient and $L$ the length of the bar. To design the controller, one has to first descretize the dynamics in $\eqref{eq:pendul_ss}$ with respect to an appropriate sample time $T_s$. Starting from an initial state, we would like the system's trajectory to converge into its equilibrium point while always $\theta\in[-\pi,\pi]$ and $\omega\in[-\pi/8,\pi/8]$. \\
	While there are many control schemes which can be used to stablize the system (e.g. LQR, state feedback), adding polytopic constraints, MPC schemes will be the best choice. 

@@

	However, one major challenge for implementing model predictive controllers over embedded systems will be to solve MPC optimality problem within each time step. Since the system under consideration is LTI, one can use explicit MPC scheme proposed in [Bemporad:2002] which computes partitions over state space together with affine functions which are used to compute the optimal control input over their corresponding partition. For the inverted-pendulum example, the computed controller contains $12$, over each an affine function is provided for generating the control input.\\

@@

	In practice, EMPC will be implemented over relatively low-price embedded systems which have limited memory capacity and computational power. Computing the optimal control input can be efficiently done using for example binary tree search. However, the memory limit is more cruicial as it increases proportional to the number of partitions.	Therefore, we would like to explore ways to reduce required memory for saving different coefficients corresponding to the controllers.
	On the other hand, most of the industrial embedded systems over which EMPC is implemented, only support fixed point arithmetic. Using fixed point arithmetic, will cause approximation error that is inversely proportional to the number of bits used for representing each variable. It is necessary to count for approximation error as it might lead into violation of the constraints. Therefore, one needs to formulate the problem as robust EMPC to count for disturbance input $|\delta|\leq \Delta$ which is summed up with the control input torque $u$ in each time step. %Setting the number of bits for storing different variables, one can compute the upper bound for approximation error, $\bar\omega$.
	%However, we would like to achieve the minimum number of bits to reduce memory requirements.
	Overlay, we would like to design a robust explicit model predictive controller, taking into account errors resulted by fixed-point arithmetic and more importantly, to come up with a set of varying precision assignment that covers all the coefficients that must be saved over the embedded system. To that end, one approach is to start with an initial $\Delta$; design a robust explicit MPC controller with respect to $\Delta$ and to use state of the art fixed-point error analyzers to decide for the number of bits for saving every parameter characterizing the controller. Figure \ref{fig:overview} gives an overview of our proposed setup.\\
	Again, back to inverted pendulum example, choosing $\Delta=0$, we design an explicit MPC which contains $12$ regions and the same number of controllers. However, this value for $\Delta$ is not realizable as error resulted from fixed-point implementation cannot become zero. Therefore, we go ahead and choose $\Delta=0.1$. Solving Robust EMPC problem for the new disturbance bound gives $14$ controllers. Next, we ask Daisy to provide us with fixed-point precisions for every variable that respects $\Delta$. Using the output of Daisy, we are able to reduce memory requirements for the embedded systems up-to $20\%$ comparing to the case that uniform fixed-point precision is used.

	\tikzstyle{block} = [draw, fill=blue!20, rectangle, 
	minimum height=3em, minimum width=6em]
	\tikzstyle{sum} = [draw, fill=blue!20, circle, node distance=1cm]
	\tikzstyle{input} = [coordinate]
	\tikzstyle{output} = [coordinate]
	\tikzstyle{pinstyle} = [pin edge={to-,thin,black}]
	\begin{figure*}[t]
		\begin{tikzpicture}[auto, node distance=2cm,>=latex',scale=1]
			\centering
			\node [block, pin={[pinstyle]above:$\delta=\delta_0$},
			node distance=5cm] (RMPC) {Robust MPC design};
			\node[] (partitions) at (2.5,.5){\includegraphics[width=.08\textwidth]{Figs/regs.jpg}};
			\node [block, right of=RMPC,
			node distance=5cm,text width=3cm] (mixed) {Mixed precision analysis};
			\node [draw, fill=blue!20, diamond, 
			minimum height=3em, minimum width=3em, right of=mixed,
			node distance=5cm] (decide) {Is memory violated?};
			\node [block, right of=decide,
			node distance=3cm] (done) {Done};
			\node [block, below of= decide,
			node distance=3cm] (delta) {increase $\delta$};

			\draw [draw,->] (RMPC) -- node [pos=-.1] {}(mixed);
			\draw [->] (mixed) -- node [name=aaa] {}(decide);
			\draw [->] (decide) -- node [above,pos=.3] {Yes} (done);
			\draw [->] (decide) -- node[pos=0.99] {} 
			node [] {No} (delta);
			\draw [->] (delta) -| node [above] {} (RMPC);

### 2019-04-02 emsoft-2019/main.tex
modified:   main.tex
some updates

%
% The first command in your LaTeX source must be the \documentclass command.
\documentclass[sigconf]{acmart}
\usepackage{listings}
\usepackage{multirow}
\usepackage{lscape}
\usepackage{amsmath}

@@

\section{Introduction}
\section{Background}
\section{Problem Description}
In this work we present an innovative method for the off-line design of robust MPC controllers (explicit), for linear time invariant systems.

To guarantee stability of the system at runtime, at design time the designer specifies the maximal disturbance value the system can tolerate: we call this numeric value \texttt{delta}. This delta has to be an upper bound for both errors generated by the system itself (e.g. noise from sensors) and disturbance coming from sources external to the system (e.g. friction).

The system is then designed to be robust against a maximal disturbance of value \texttt{delta}.

Among the sources of disturbance targeting the controller, our goal is to assure that the approximation error caused by the use of finite precision arithmetic is also bounded by this design value \texttt{delta}.

In particular, (i) first we want to guarantee that the finite precision implementation of the controller produces an approximation error that is at most equal to delta.

(ii) Second, we want to take advantage of this disturbance delta, and reduce the arithmetic precision used for computations and storage, while still guarantee that the approximation error generated is bounded by delta. Our intuition is that a greater value for delta allows for a reduced precision for computations (e.g. with respect to 32bits).

Given an initial delta, we design the controller by solving an off-line optimization problem. We rely on MATLAB multi-parametric toolbox to solve such optimization problem~\cite{matlabMPT, matlabYALMIP}. 
The output of the suite is a continuous piecewise affine (PWA) function, together with a partitioning of the domain of \statevarmath. Each element in this partitioning is called a region.
A generic region $i$ consists in a n-polytope, uniquely identified by a set of inequalities $H_{i}\statevar<=K_{i}$.

We call \statespace\space the union of all regions $i$ is the domain of the state variable $x_{k}$:
\begin{equation}
\statespace = \bigcup_{i}(H_{i}\statevar<=K_{i})
\end{equation}

Each region $i$ is associated with an activation function $u_{i,k}=F_{i}x_{k}+G_{i}$.

%https://en.wikipedia.org/wiki/Polyhedron
%https://en.wikipedia.org/wiki/Polytope

A drawback in the design of explicit MPC is that both regions boundaries (H and K) and activation functions (F and G), have to be stored on the micro-controller. Usually these devices have limited memory in the order of KBs.

At runtime, the value of state variable \statevarmath  is compared against the polytopes bounds stored on the device: depending on the region containing \statevarmath, the corresponding activation function is computed.

This work does not rely on any specific technique to verify which region \statevarmath belongs to, so we consider a linear search over all the regions in \statespace\space, using a case-of conditional statement similar to the one in Listing \ref{lst:caseof}.

\begin{lstlisting}[escapeinside={(*}{*)},label={lst:caseof}, caption=switch for region selection]
switch((*\statevarmath*)):
  case (*$ H_{1}\statevar<=K_{1}$*) then (*$u_{1}$*)
  case (*$ H_{2}\statevar<=K_{2}$*) then (*$u_{2}$*)
  case (*$ H_{3}\statevar<=K_{3}$*) then (*$u_{3}$*)
  ...
  case (*$ H_{n}\statevar<=K_{n}$*) then (*$u_{n}$*)
\end{lstlisting}

\section{Error Analysis}
Since (i) any measurement of the plant comes with some uncertainty (e.g. uncertainty from sensors) but also (ii) due to analog-digital conversion, the value of state variable \statevarmath comes with some numerical errors. The equation for \statevarmath is than defined as:
\begin{equation}
\qstatevar=\statevar + \texttt{err}
\end{equation}
where \statevarmath is the true (unknown) measure of the plant, while \qstatevarmath is the actual value.

\texttt{err} generates instability when it is time to verify which region \qstatevarmath belongs to: given the value of \statevarmath the region should be $i$, but because of \texttt{err}, actually region $j$ is selected. This scenario becomes more intuitive when \qstatevarmath falls \texttt{close} to the border between two generic regions $i$ and $j$, but in general it depends on the magnitude of \texttt{err}.

Assuming that all points in region $i$ might be erroneously assigned to region $j$, without any  knowledge of the actual value of error \texttt{err}, is a too wide over-approximation of the existing instability.

Our goal is to build a feasible geometrical space around the border between regions $i$ and $j$, where actually it is feasible that \statevarmath belongs to region $i$ but \qstatevarmath follows in region $j$.

We call this geometrical space the \texttt{tube}.

There are two main sources of error affecting the size of the \texttt{tube}: (i) the first one is caused by analog-digital conversion, happening just before the controller receives an estimation of the plant from the sensors. We call this error $\varepsilon_{A/D}$:

\begin{equation}\nonumber
\varepsilon_{A/D}=\frac{V_{cc}}{2^{p}-1}
\end{equation}

Where $V_{cc}$ is the reference voltage of the converter (e.g. typical 5V) and $p$ represents the number of bit of the processor.

The second error affecting the size of the \texttt{tube} is caused by (ii) the quantization of region bounds in the memory of the micro-controller. We call this error $\varepsilon_{Q}$ for error quantization.

While $\varepsilon_{A/D}$ is intrinsic in the capabilities of the device, $\varepsilon_{Q}$ depends on the precision used to store the boundaries. This second error can be regulated based on a trade-off among accuracy of the storage and memory save~\cite{memoryMPC}.

The total size of the \texttt{tube} is then:
\begin{equation}\label{eq:epsilontot}
\varepsilon=\varepsilon_{A/D}+\varepsilon_{Q}
\end{equation}
\section{Finite Precision Implementation}
The output of the controller can be affected by two main errors: (i) the controller chooses the wrong activation function because of $\varepsilon$ in (\ref{eq:epsilontot}), while (ii) is the approximation error deriving from the finite precision arithmetic used to compute the activation function itself~\cite{imperialrmpc}.

The effect of selecting the wrong activation function are similar to instability in the switch reported in Listing \ref{lst:caseof}. Suppose an hypothetic scenario where all the measurements were done in infinite precision and without any uncertainty: the controller $i$ would be activated.

Instead, because of these limitations controller $j$ is selected. The resulting error is then the difference between the output of the two branches $i$ and $j$.

The system has to be robust against a mistake in choosing controller $i$ instead of $j$ (or vice-versa) only when \qstatevarmath falls into the \texttt{tube} between $i$ and $j$, and not for all the points in the two regions.

In the following, we assume $i$ and $j$ are the index of two generic regions in \statespace:
\begin{flalign}
\label{eq:maximization}
&\max_{\forall i,j\;|\;neighbour(i,j)}|u_{i}-u_{j}| = \\
&\max_{\forall i,j\;|\;neighbour(i,j)}|F_{i}\statevar+G_{i} - (F_{j}\statevar+G_{j})|\nonumber
\end{flalign}

Because of the linearity of the function $u_{i}-u_{j}$, and because of the convexity of the regions $i$, $j$ it is enough to evaluate function (\ref{eq:maximization}) at the corners of the \texttt{tube}.

%The geometrical space where $\hat{X}$ activates $U_{i}$, while X would activate $U_{j}$ can be bounded thanks to a preliminary knowledge of the error $\varepsilon$: the distance between region $i$ and $j$ such that:
%\begin{equation}
%\hat{X}-X <= \varepsilon
%\end{equation}
%and $\hat{X}$ belongs to region $i$ but $X$ to $j$ (or vice-versa).

We compute (\ref{eq:maximization}) for all pairs of neighbor regions $i$ and $j$. Two regions are neighbors when they share at least a border.

In formula $\exists\; m,n \;$such that:
\begin{equation}
(H_{i}\statevar-K_{j})_{m} = (H_{j}\statevar-K_{j})_{n}
\end{equation}
where $m$ and $n$ are the index of the two matching borders. We label with $border_{i,j}$ the matching border shared among the two regions.

Starting from the equation of $border_{i,j}$, we delimit the geometrical space where it makes sense to compute (\ref{eq:maximization}) with: 
\begin{equation}
\begin{aligned}
border_{i,j} >= -\varepsilon\\
border_{i,j} <= \varepsilon
\end{aligned} 
\end{equation}
where $\varepsilon$ is defined in (\ref{eq:epsilontot}).

We call such geometrical space the \texttt{tube} between $i$ and $j$.

When \qstatevarmath belongs to the \texttt{tube}, it might be that $u_{i}$ is activated instead of $u_{j}$ (or vice-versa). Otherwise, when \qstatevarmath does not belong to the tube, no matter the error \texttt{err}, the right activation function is activated, and we consider only the error deriving from the computation itself.

Since computing $u_{i}$ introduces approximation error because of finite precision arithmetic, the system has to be robust against an error that is:

\begin{equation}\label{eq:fperror}
err(u_{i})_{p}=|(\hat{F}_{p}-F)\qstatevar+(\hat{G}_{p}-G)|
\end{equation}

where $\hat{F}$ and $\hat{G}$ represent the rounded values (in p bits) for the infinite precision values $F$ and $G$.

In (7) the domain of \qstatevarmath are all the points in region $i$, but also all the values in the \texttt{tube} between region $i$ and any of the neighbors of $i$. Even for values that do not belong to region $i$ it might be the case that $u_{i}$ is (erroneously) activated. In particular, this is true for values in the \texttt{tube}.

We compute (\ref{eq:fperror}) for all regions in \statespace\space and we take the maximum value:

\begin{equation}\label{eq:maxfperror}
\max_{\forall \regionimath{i}\;in\;\statespace} err(u_{i})_{p}
\end{equation}

The disturbance \texttt{delta} then has to be an upper bound to the summation of (\ref{eq:maximization}) and (\ref{eq:fperror}).

In formula:
\begin{flalign}
\label{eq:delta}
&delta >= \\
&\max_{\forall i,j\;|\;neighbour(i,j)}|u_{i}-u_{j}| + \max_{\forall\;\regionimath{i}\;in\;\statespace} err(u_{i})_{p}\nonumber
\end{flalign}

\section{Precision Tuning}
In formula (\ref{eq:epsilontot}), the equation for $\varepsilon$ contains: $\varepsilon_{A/D}$ that is the error introduced by the analog-digital conversion, and $\varepsilon_{Q}$ that is generated by the quantization of hyperplanes $H\statevar<=K$ in a finite number of bits.
This $\varepsilon_{Q}$ can be tuned based on memory availability in the micro-controller.
The rule for $\varepsilon_{Q}$ is the following:
\begin{equation}\label{eq:quantizationlines}
\varepsilon_{Q} > (H-(\hat{H})_{p})\qstatevar+(K-(\hat{K})_{p})
\end{equation}
This inequality assures that the distance between any hyperplane represented in infinite precision, and its counter-part quantized in p bits, is bounded by $\varepsilon_{Q}$.

Our goal is to solve (\ref{eq:quantizationlines}) with respect to p: find the minimal-precision p such that the inequality holds.

The main advantage in doing this (compared to fixing the precision a priori), is that the value of p can be tuned based on the memory available in the micro-controller.

To solve (\ref{eq:quantizationlines}) we used Daisy: a static analyzer for finite precision expressions, able to provide a sound upper-bound to the maximal approximation error of an expression with respect to its real (infinite precision) counterpart. Since the magnitude of the round-off error depends on the range of input variables, any variable encoded in Daisy has to be bounded.

Since the state variable \statevarmath is bounded, and F,G,H, and K are vectors of constants, we can rely on Daisy for this verification step.

In a similar way, we use Daisy to solve the inequality in (\ref{eq:delta}) with respect to p.

\begin{flalign}
\label{eq:deltaminusmax}
&delta - \Big(\max_{\forall i,j\;|\;neighbour(i,j)}|u_{i}-u_{j}|\Big)>=\\
& \max_{\forall\;\regionimath{i}\;in\;\statespace} err(u_{i})_{p}\nonumber
\end{flalign}
We want to point out that the left side of the inequality is not parametrized in p. Only the right size of (\ref{eq:deltaminusmax}) actually depends on the precision p. We encode the inequality (\ref{eq:deltaminusmax}) in Daisy, to detect what is the minimal precision that satisfy the inequality.

\section{Algorithm}

\begin{lstlisting}[language=Python,numbers=left,numbersep=3pt,frame=lines,keepspaces=true,escapeinside={(*}{*)},caption=design of robust MPC with verification and precision tuning,label={lst:alg}]
 delta=input()
 (*$\varepsilon_{Q}$*)=input()
 assert (delta>=0 and (*$\varepsilon_{Q}$*)>0)
 epsilon=(*$\varepsilon_{A/D}$*)+(*$\varepsilon_{Q}$*) #size of the tubes

 while True:
   design_robust_MPC(delta)
   maxUij = compute (*(\ref{eq:maximization})*) with size(tube)=(*$\varepsilon$*)
   if delta > maxUij:
     max_err=delta-maxUij
     UNI_MIX_precision(F,G,max_err)
     UNI_MIX_precision(H,K,(*$\varepsilon_{Q}$*))
     break
   else:
     delta=maxUij+(*$\varepsilon_{SAFE}$*)

\end{lstlisting}
In Listing \ref{lst:alg} we describe the procedure used to design an MPC controller robust to both (\ref{eq:maximization}) and (\ref{eq:maxfperror}).

First, the designer fixes the initial values for delta and $\varepsilon_{Q}$.

Even if it possible to assign value zero to delta~\cite{imperialrmpc}, we do not encourage such initialization: it is going to fail the analysis at least once because the error in (\ref{eq:maxfperror}) is going to be greater than zero (even in case (\ref{eq:maximization}) is zero). A better initialization would be to set delta to an arbitrary small value, slightly greater than zero.

On the other hand, the value for $\varepsilon_{Q}$ has to be strictly greater than zero, otherwise we could rely on infinite precision for p in (\ref{eq:quantizationlines}).

Once input parameters are verified, we use MATLAB toolbox to design a controller with robustness value equal to delta.

Then, we compute (\ref{eq:maximization}) and we compare the result with delta: we are aware that the computation of (\ref{eq:maximization}) is not exact (even if it is done in 64bits precision), but usually the computation of (\ref{eq:maximization}) results in a value that is several orders of magnitude greater than the error of the computation itself. For this reason we consider this approximation error negligible from the point of view of our analysis.

Again, in the conditional inside the loop, delta has to be strictly greater than \texttt{maxUij} otherwise we do not have space for computing the precision for (\ref{eq:deltaminusmax}).

In case the conditional statement is verified,
the precision tuning phase starts.
For the precision tuning of activation functions, we allow an error that is bounded by \texttt{max\_err}. This is because we still need to satisfy (\ref{eq:delta}).
On the other hand, the quantization of polytopes borders (the region bounds in \statespace) can produce an error that is at most $\varepsilon_{Q}$, in this way we satisfy 
(\ref{eq:quantizationlines}).

In case the conditional fails and \texttt{maxUij} is greater than delta, the controller needs to be re-designed with a robustness value that is at least equal to the current value of \texttt{maxUij}. The same consideration done for the initialization of input parameters holds also here: the constant $\varepsilon_{SAFE}$ is used to relax the value delta for the controller, to a value slightly greater than \texttt{maxUij}. In this way, we aim to give some space to the precision tuning phase in the next iteration of the loop. Otherwise, in case of $\varepsilon_{SAFE}$ equal to zero, the next iteration of the precision tuning phase is going to require unnecessarily wide precision values p, usually greater than 32 bits. 
We remark that the point of the analysis is to find a low precision configuration for bounds and activation functions: in case the analysis outputs a precision greater than 32bits, we fail in our goal.
Then, with a minimal alteration to the upper bound of delta, we sensibly reduce the precision needed for $F$ and $G$, with respect to the standard 32 bits precision.

\section{Experimental Results}

\subsection{Case of study: Inverted Pendulum}
%\begin{landscape}
%\begin{table*}[t]
%	\centering
%	\caption{Inverted Pendolum: delta}
%	\label{tab:ipd}
%	\begin{tabular}{r|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r}
%		\multicolumn{4}{c}{} &
%		\multicolumn{2}{c}{Xbounds} &
%		\multicolumn{2}{c}{} &
%		\multicolumn{4}{c}{F and G} &
%		\multicolumn{4}{c}{H and K} 
%		\\
%		\multicolumn{1}{c}{delta}&
%		\multicolumn{1}{c}{eps} &
%		\multicolumn{1}{c}{regs} &
%		\multicolumn{1}{c}{hyps} &
%		\multicolumn{1}{c}{X0}&
%		\multicolumn{1}{c}{X1}&
%		\multicolumn{1}{c}{max\_Uij} &
%		\multicolumn{1}{c}{err} &
%		\multicolumn{1}{c}{tot.uni32}&
%		\multicolumn{1}{c}{tot.uni}&
%		\multicolumn{1}{c}{tot.mix}&
%		\multicolumn{1}{c}{\% saved}&
%		\multicolumn{1}{c}{tot.uni32}&
%		\multicolumn{1}{c}{tot.uni}&
%		\multicolumn{1}{c}{tot.mix}&
%		\multicolumn{1}{c}{\% saved}
%		%\multicolumn{1}{c}{\multirow{2}{*}{max|Ui-Uj|}} &
%		%\multicolumn{1}{c}{\multirow{2}{*}{FP\_err}} &
%		%\multicolumn{4}{c}{F and G} &
%		%\multicolumn{4}{c}{H and K} \\
%		%\cline{5-6}\cline{9-12}\cline{13-16} &
%		%\multicolumn{1}{c}{X0}
%		%\multicolumn{1}{c}{X1} &
%		
%	\end{tabular}
%\end{table*}
%\end{landscape}

\subsection{Case of study: 4d example}
\section{Related Work}
\section{Conclusions}

%\begin{table*}
%  \caption{Some Typical Commands}
%  \label{tab:commands}
%  \begin{tabular}{ccl}
%    \toprule
%    Command &A Number & Comments\\
%    \midrule
%    \texttt{{\char'134}author} & 100& Author \\
%    \texttt{{\char'134}table}& 300 & For tables\\
%    \texttt{{\char'134}table*}& 400& For wider tables\\
%    \bottomrule
%  \end{tabular}
%\end{table*}

%\begin{figure}[h]
%  \centering
%  \includegraphics[width=\linewidth]{sample-franklin}
%  \caption{1907 Franklin Model D roadster. Photograph by Harris \& Ewing, Inc. [Public domain], via Wikimedia Commons. (\url{https://goo.gl/VLCRBB}).}
%  \Description{The 1907 Franklin Model D roadster.}
%\end{figure}

%Some examples.  A paginated journal article \cite{Abril07}, an enumerated journal article \cite{Cohen07}, a reference to an entire issue \cite{JCohen96}, a monograph (whole book) \cite{Kosiur01}, a monograph/whole book in a series (see 2a in spec. document)

>>>>

%
% The first command in your LaTeX source must be the \documentclass command.
\documentclass[sigconf]{acmart}
\usepackage{listings}
\usepackage{multirow}
\usepackage{lscape}
\usepackage{amsmath}
\usepackage{tikz}
\usetikzlibrary{shapes,arrows}
\usepackage{graphicx}

@@

\input{intro}
\input{motiv}
\input{RMPC_Daisy}
\input{Methodology}
\input{experiments}
\input{Conclusion}
